Before there were computers, there were algorithms. But now that there are computers, there are even more algorithms, and algorithms lie at the heart of computing\\
In the domain of mathematics and computer science, graph theory is the study of graphs that concerns the relationship among edges and vertices.\\
In recent years, graph theory has established itself as an important mathematical tool in a wide variety of subjects, ranging from operational research and chemistry to genetics and linguistics, and from electrical engineering and geography to sociology and architecture. At the same time it has also emerged as a worthwhile mathematical discipline in its own right.

\subsubsection*{About the report}
\addcontentsline{toc}{subsection}{About the report}
This work is written as a part of the Summer Of Science, 2020 project organized by the MnP Club, IIT Bombay. (Mentor: Tathagat Verma)\\
I have followed the course MIT 6.042J/18.062J and MIT 6.006 offered by MIT. The report consists mainly of my notes for these lectures.\\
All content here is highly inspired by the courses and at several points might simply be a paraphrasing of the course content. Nevertheless, I have tried to compress the contents of the course, skipping a few of the details, while still preserving sufficient depth.\\
\vspace{3mm}
Prerequisites for understanding the content:\\
\vspace{-3mm}
\begin{itemize}[itemsep = -1 mm]
  \item You should have some programming experience. In particular, you should understand recursive procedures and simple data structures such as arrays and linked lists.
  \item You should have some facility with mathematical proofs, and especially proofs by mathematical induction.
\end{itemize}
Though it may be hard to believe for a report of this size, space constraints prevented me from including many interesting algorithms and problems.

\subsubsection*{About the project and its future}
\addcontentsline{toc}{subsection}{About the project and its future}
Even after completion of SoS 2020, I intend to learn further in this field.\\
I would be moving on to MIT 6.046J/18.410J (Design and Analysis of Algorithms) and MIT 6.854J/18.415J (Advanced Algorithms - a Graduate level course).\\
More courses in this context are MIT 6.045J/18.400J, MIT 18.404J/6.840J, MIT 6.079/6.975, MIT 18.315.\\
